### 2013-01-19 edupar-13/410.tex
410.tex: Squeeze pass over "Grading" section.

While developing their code, students uncover both bugs
and design misunderstandings by running test code we
provide.
%Some tests are simple, exercising one feature or condition
%(e.g., allocating and freeing a large amount of memory),
%while other tests exercise a mix of kernel features
%simultaneously (creating and destroying processes,
%some of which do I/O while others handle or are killed
%by various exceptions) over an extended period of time.
The test suite is a number of user-space programs which test
functionality ranging from the basic process lifecycle, to robustness
against corner-case security vulnerabilities, to long-term stability
under large stress tests.
%
When students submit their kernels,
we use an automated testing harness to
run a superset of the public test suite.
%
Of course, due to the nondeterministic nature of many common bugs in student code,
these tests can provide only a rough estimate of a submission's correctness,
rather than verifying it with certainty.
(This hit-or-miss nature motivated our work on Landslide.)
Nevertheless, performance on these tests constitutes 30\% of the kernel project's grade.

@@

\item We believe that students learn more from bugs
that are harder to find.
In extreme cases, a software component may do
``almost everything right,'' but ``the last bug'' may
demonstrate a deep misunderstanding which requires a re-design.

@@

For these reasons, we believe much of the learning
associated with the kernel project necessarily occurs
at the end of the experience,
so it is important for students to finish the process.
% [suppressed: bad to build P4 on a shaky P3]
We believe it would be particularly detrimental to
assign ``partial credit'' to a large body of non-working
code.
Instead, we require student kernels to pass a
specified percentage of each segment of the test
suite to be considered complete.
Furthermore,
because the test suite cannot detect certain
structural shortcuts (e.g., papering over a concurrency
problem by disabling interrupts during \textit{all}
kernel execution),
we require students to certify, in writing, that
their code possesses certain properties.

A ``complete'' kernel can boot up and run the shell,
can pass 80\% of the basic system-call sanity test,
can pass 70\% of the ``solidity'' tests (which
invoke system calls in illegal or non-trivial ways),
and can pass two of the three long-running multi-feature tests.
In addition,
a complete kernel is certified by the authors to
be free of ``concurrency shortcuts,''
to handle resource exhaustion,
and to avoid certain distasteful x86-specific code structures.
%
% The hurdle is a set of criteria that Pebbles implementations must meet to be considered sastisfactory
% (TODO: what are they?).
%Towards the end of the kernel project, students fill out the ``hurdle form'', a checklist of these criteria.
Students who pass the completeness ``hurdle'' submit their kernels
and can move on to the ``Pebbles Extension'' project.
Meanwhile, students who were unable to meet the
hurdle criteria on time receive additional time
to finish up and improve their code quality.
%---this
%requirement is based on our belief that important
%learning experiences are obtained by solving the
%hard problems,
%which turn up at the end of the kernel implementation.
The hurdle criteria constitute 50\% of the kernel project's grade.

@@

Finally, both to make up for the tests' incompleteness and to provide personalized human feedback, each student kernel is manually graded by a member of course staff.
The instructors and teaching assistants print out each group's submitted kernel and mark it with red ink, auditing the code for style, architectural issues, race conditions, and preemptibility.
After the inking process, each group meets with the staff member who graded them for an hour-long ``kernel interview'', essentially a debriefing in which any final misconceptions the students might have can be rectified.
Staff discretionary points constitute 20\% of the kernel project's grade.

>>>>

While developing their code, students uncover both bugs
and design misunderstandings by running test code we
provide.
%Some tests are simple, exercising one feature or condition
%(e.g., allocating and freeing a large amount of memory),
%while other tests exercise a mix of kernel features
%simultaneously (creating and destroying processes,
%some of which do I/O while others handle or are killed
%by various exceptions) over an extended period of time.
The test suite is a number of user-space programs which test
functionality
including the basic process lifecycle, robustness
against corner-case security vulnerabilities, and long-term stability
under large stress tests.
%
When students submit their kernels,
we use an automated testing harness to
run a superset of the public test suite.
%
Of course, due to the nondeterministic nature of many bugs in student code,
these tests can provide only a rough estimate of a submission's correctness,
rather than verifying it with certainty.
(This hit-or-miss nature motivated our work on Landslide.)
Nevertheless, performance on these tests constitutes 30\% of the kernel project's grade.

@@

\item \shortversion{Students}{We believe that students} learn more from bugs
that are harder to find.
In extreme cases, a software component may do
``almost everything right,'' but ``the last bug'' may
demonstrate a deep misunderstanding which requires a re-design.

@@

For these reasons, \shortversion{}{we believe} much of the learning
associated with the kernel project necessarily occurs
at the end of the experience,
so it is important for students to finish the process.
% [suppressed: bad to build P4 on a shaky P3]
\shortversion{It}{We believe it} would be particularly detrimental to
assign ``partial credit'' to a large body of non-working
code.
Instead, we require student kernels to pass a
specified percentage of each segment of the test
suite to be considered complete.
Furthermore,
because the test suite cannot detect certain
structural shortcuts (e.g., papering over a concurrency
problem by disabling interrupts during \textit{all}
kernel execution),
we require students to certify, in writing, that
their code possesses certain properties.

A ``complete'' kernel can boot up and run the shell,
can pass 80\% of the basic system-call sanity test,
can pass 70\% of the ``solidity'' tests (which
invoke system calls in illegal or non-trivial ways),
and can pass two of the three long-running multi-feature tests.
In addition,
a complete kernel is certified by the authors to
be free of ``concurrency shortcuts,''
to handle resource exhaustion,
and to avoid certain distasteful x86-specific code structures.
%
% The hurdle is a set of criteria that Pebbles implementations must meet to be considered sastisfactory
% (TODO: what are they?).
%Towards the end of the kernel project, students fill out the ``hurdle form'', a checklist of these criteria.
Students who pass the completeness ``hurdle'' submit their kernels
and can move on to the kernel-extension project.
\shortversion{Students}{Meanwhile, students} who were unable to meet the
hurdle criteria on time receive additional time
to finish up and improve their code quality.
%---this
%requirement is based on our belief that important
%learning experiences are obtained by solving the
%hard problems,
%which turn up at the end of the kernel implementation.
The hurdle criteria constitute 50\% of the kernel project's grade.

@@

Finally, both to make up for the tests' incompleteness and to provide personalized human feedback, each student kernel is manually graded by a member of course staff.
The instructors and teaching assistants print each group's submitted kernel and mark it with red ink, auditing the code for style, architectural issues, race conditions, and preemptibility.
After the inking process, each group meets with \shortversion{their grader}{the staff member who graded them} for an hour-long ``kernel interview,'' essentially a debriefing in which student misconceptions can be rectified.
Staff discretionary points constitute 20\% of the kernel project's grade.
